\bf Adaptive Mesh Refinement for 1-D Hyperbolic PDEs

### 2015-03-08 paper_draft1.tex
paper -changed outline slightly and edited

\subsection{Flux updates on refined and coarse meshes}
After finishing the recursive step creating the fine grid structure, how to evolve the newly refined grid needs to be considered. To evolve, conservation of fluxes at grid interfaces is required. We refer to Fig \ref{fig21} for this discussion. There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and overlapping coarse cell and fine cell regions. Let $F_i$ be the flux at the left edge of coarse cell $i$. This is different notation than what we typically wrote in class, $F_{i-\frac{1}{2}}$. 
\begin{figure}[h]
    \centering
    \includegraphics[width=.6\textwidth]{berg-lev-fig21}
   \caption{Essential figure for flux adapting Cartesian grids. The top grid is the normal coarse grid we are used to using with fluxes indicated. The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids. Recall that $2\hat{h}=h$ and $2\hat{k}=k$. The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
    \label{fig21}
\end{figure}

>>>>

\subsection{flux updates on refined and coarse meshes}
After finishing the recursive step creating the fine grid structure, how to evolve the newly refined grid needs to be considered. To evolve, conservation of fluxes at grid interfaces is required. We refer to Fig \ref{fig21} for this discussion. There are essentially three cases to consider: coarse cell to coarse cell, fine cell to fine cell, and overlapping coarse cell and fine cell regions. Let $F_i$ be the flux at the left edge of coarse cell $i$. This is different notation than what we typically wrote in class, $F_{i-\frac{1}{2}}$. 
\begin{figure}[h]
    \centering
    \includegraphics[width=.6\textwidth]{berg-lev-fig21}
   \caption{Essential figure for flux adapting Cartesian grids. The top grid is the normal coarse grid we are used to using with fluxes indicated. The middle diagram shows the case where a fine grid overlays a coarse grid and the interface region of fine and coarse grids. Recall that $2\hat{h}=h$ and $2\hat{k}=k$. The bottom diagram depicts the ghost cell region imposed on the coarse cell interface as well as the fine grid fluxes needed to bridge the interface.}
    \label{fig21}
\end{figure}
